\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-11-08 response2.tex
Just noticed issue with definitions
minor comments

It may be worth noting explicitly that you allow d-framed graphs to
have edges outside the outer face of their frame - I was unsure about
this given the phrase “interior of the face”.

>>>>

It may be worth noting explicitly that you allow $d$-framed graphs to
have edges outside the outer face of their frame - I was unsure about
this given the phrase “interior of the face”.

\tba
